%
% File acl2019.tex
%
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage{authblk}
\usepackage[hyperref]{acl2019}
\usepackage{times}
\usepackage{IEEEtrantools}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{mathtools}

\usepackage{multirow}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[inline]{enumitem}
\usepackage{bm}
\usepackage{caption}


\usepackage{url}

\aclfinalcopy % Uncomment this line for the final submission
\def\aclpaperid{890} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

%\title{Joint Entity Relation Extraction with Graph Convolutional Network}
\title{Joint Type Inference on Entities and Relations via Graph Convolutional Networks}
%\title{End-to-End Neural Relation Extraction with Joint Type Inference}
%\title{Joint Type Inference for Extracting Entities and Relations}

%\author{First Author \\
%  Affiliation / Address line 1 \\
%  Affiliation / Address line 2 \\
%  Affiliation / Address line 3 \\
%  \texttt{email@domain} \\\And
%  Second Author \\
%  Affiliation / Address line 1 \\
%  Affiliation / Address line 2 \\
%  Affiliation / Address line 3 \\
%  \texttt{email@domain} \\}

\author[1, \thanks{\ \ \ Work done while this author was an intern at Microsoft Research Asia.}]{\bf Changzhi Sun  }
\author[2]{\bf Yeyun Gong}
\author[1, 3]{\bf Yuanbin Wu}
\author[2]{\bf Ming Gong}
\author[2]{\bf Daxing Jiang}
\author[1]{\\ \bf Man Lan}
\author[1]{\bf Shiliang Sun}
\author[2]{\bf Nan Duan}
\affil[1]{Department of Computer Science and Technology, East China Normal University}
\affil[2]{Microsoft Research Asia}
\affil[3]{State Key Laboratory of Cognitive Intelligence, iFLYTEK}
\affil[  ]{\tt \{changzhisun\}@stu.ecnu.edu.cn \{ybwu,mlan,slsun\}@cs.ecnu.edu.cn}
%\affil[ ]{\tt \{ybwu,mlan,slsun\}@cs.ecnu.edu.cn}
\affil[  ]{\tt \{yegong, nanduan, migon, djiang\}@microsoft.com}


\begin{document}
\maketitle
\begin{abstract}
  We develop a new paradigm for the task of joint entity relation extraction.
  It first identifies entity spans,
  then performs a joint inference on entity types and relation types.
  To tackle the joint type inference task,
  we propose a novel graph convolutional network (GCN)
  running on an entity-relation bipartite graph.
  By introducing a binary relation classification task,
  we are able to utilize the structure of entity-relation  bipartite graph in a more efficient and interpretable way.
  Experiments on ACE05 show that our
  model outperforms existing joint models in entity performance
  and is competitive with the state-of-the-art in relation performance.
\end{abstract}

\input{intro}
\input{approach}
\input{experiments}
\input{related_work}

\section{Conclusion}
We propose a novel and concise joint model
based on GCN
to perform joint type inference
for entity relation extraction task.
Compared with existing joint methods,
it provides a new way to 
capture the interactions on multiple entity types and relation types explicitly in a sentence.
%By introducing a binary relation classification task,
%our method could utilize the structure of entity-relation bipartite graph in a more efficient and interpretable way.
Experiments on ACE05
dataset show the effectiveness of the proposed method.

\section*{Acknowledgement}

The authors wish to thank the reviewers for their helpful
comments and suggestions.
This research is (partially) supported by
STCSM (18ZR1411500), NSFC(61673179) and the Foundation of State Key Laboratory of Cognitive Intelligence, iFLYTEK(COGOS-20190003).
The corresponding authors are Yuanbin Wu and Shiliang Sun.

\bibliography{acl2019}
\bibliographystyle{acl_natbib}

\end{document}
